\documentclass{article}
\usepackage{ou-tma}

\begin{document}

    \typeout{ [DRV] Theorem: no tag, no auto-label}
    \begin{Theorem}
        This theorem will have automatic numbering.
    \end{Theorem}

    \typeout{ [DRV] Theorem: tag, auto-label}
    \begin{Theorem}[B35]
        This theorem will use the tag "B35" and suppress numbering.
    \end{Theorem}

    \typeout{ [DRV] Theorem: no tag, no auto-label}
    \begin{Theorem}
        Ordinary theorem. Numbered, but no auto-label.
    \end{Theorem}

    \typeout{ [DRV] Theorem: no tag, no auto-label}
    \begin{Theorem}
        This theorem will have no auto-label.
    \end{Theorem}

    \typeout{ [DRV] Theorem: tagged, auto-label}
    \begin{Theorem}[B36]
        Tagged theorem. Tag printed, label auto-sanitised.
    \end{Theorem}

    \typeout{ [DRV] Theorem: no tag, no auto-label}
    \begin{Theorem}
        Back to the ordinary. Numbered and not auto-labelled.
    \end{Theorem}

    \typeout{ [DRV] Reference to Theorem B36 auto-label}
    See \Cref{thm:b35} for reference.

    \typeout{ [DRV] Lemma: no tag, no auto-label}
    \begin{Lemma}
        This is a Lemma, look how its fur glistens. Numbered but with no auto-label.
    \end{Lemma}

    \typeout{ [DRV] Lemma: tagged, auto-label}
    \begin{Lemma}[Famous]
        If there was ever such a well known Lemma, this is it! Tagged and auto-labelled.
    \end{Lemma}

    \typeout{ [DRV] Theorem: no tag, no auto-label}
    \begin{Theorem}
        Oh there must be another numbered Theorem without tag or label!
    \end{Theorem}

    \typeout{ [DRV] Reference to Lemma Famous auto-label}
    See \cref{lem:famous} for reference

\end{document}
